---
title: Understanding Prime Mover(PM) Productivity in Yard
author:
  - name: Li Zhenglong
  - name: Lim Kai Chin
affiliation: Singapore Management University

column_numbers: 3
poster_width: "23.39in"
poster_height: "33.11in"
title_textsize: "50pt"
author_textsize: "32pt"
affiliation_textsize: "32pt"
body_textsize: "24pt"
sectitle_textsize: "32pt"
sectitle2_textsize: "28pt"


#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

# Motivation and objectives

Our research and development effort were motivated by the general lack of effective and easy to use web-enabled data visualization tool to conduct data analysis on PM operation data. The project aims to enable operation managers the ability to monitor,drill down and identify key attributes contributing to the PM productivity.

# Approach
Approach - A description of the techniques or algorithms you used to solve the problem.
Datawrangling
Data Transformation
Data exploration

Results - Screenshots and a working demo of the system you built.
# EDA

# CDA

# Quality Improvement
## Pareto Chart 
## Control Chart






# Future Work 
An explanation of how the work could be extended.

```{r}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
