---
title: Understanding Prime Mover(PM) Productivity in Yard
author:
  - name: Li Zhenglong
  - name: Lim Kai Chin
affiliation: Singapore Management University

column_numbers: 3
poster_width: "23.39in"
poster_height: "33.11in"
title_textsize: "50pt"
author_textsize: "32pt"
affiliation_textsize: "32pt"
body_textsize: "24pt"
sectitle_textsize: "32pt"
sectitle2_textsize: "28pt"


#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

# Motivation and objectives
issues and problems - A clear statement of the issues or/and problems your project addresses.
Motivation - An explanation of why the issues and/or problems are interesting and what make them difficult to solve.

# Approach
Approach - A description of the techniques or algorithms you used to solve the problem.
Datawrangling
Data Transformation
Data exploration

Results - Screenshots and a working demo of the system you built.
# EDA

# CDA

# Quality Improvement
## Pareto Chart 
## Control Chart






# Future Work 
An explanation of how the work could be extended.

```{r}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
